Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces for downstream MIR tasks

### 2023-03-10 introduction/Subsections/Introduction.tex
Updates from Overleaf

The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream tasks. Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries. Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard. Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.

>>>>

The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream music information retrieval (MIR) tasks. Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries. Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard. Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.

### 2023-03-10 introduction/Subsections/Objectives.tex
Updates from Overleaf

As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data. I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information. By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis. By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.

>>>>

As a professional music transcriber myself, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data. I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information. By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis. By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.

### 2023-03-10 methods/methods.tex
Updates from Overleaf

\section{Materials}

\section{Convolutional Neural Network (CNN)}

A CNN, or Convolutional Neural Network, is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:

\begin{itemize}

\item Convolutional layers: These layers apply a convolution operation to the input data, effectively learning local patterns and features in the image. The raw audio data is typically transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data. The convolutional layers are designed to learn local patterns and features in the audio data
\vspace*{3mm}

\item Pooling layers: These layers downsample the data, reducing the spatial dimensions of the input while retaining important information. They can also be used to downsample the data and reduce the temporal dimensions of the input while retaining important information. 
\vspace*{3mm}

\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another layer, allowing the network to learn non-linear combinations of the features learned in the previous layers.
\vspace*{3mm}

\item Output layer: The output layer produces the final predictions of the network.
\end{itemize}

Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train. This makes them more feasible for large-scale datasets and real-world problems.

On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not be able to do effectively.

\subsection{Neural Network (NN)}

%Single
\input{Figures/Figures CNN/Single Neuron}
%NN
\input{Figures/Figures CNN/Network_graph}

%Backpropagation
\input{Figures/Figures CNN/Multi-layer_NN}

%CNN
A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details (number of channels or neurons per layer or the input image size) can be seen in XXX.
\input{Figures/Figures CNN/CNN_diagram}

%Single CNN
\input{Figures/Figures CNN/Single_CNN}

%Single pooling layer
\input{Figures/Figures CNN/Single_Pooling_Layer}

%Backpropagation
\input{Figures/Figures CNN/Back_propagation}

\newpage

>>>>

\section{Materials}
\input{methods/subsections/model}

\section{Convolutional Neural Network (CNN)}
\input{methods/subsections/test}
\newpage
